---
title: "Lab1"
author: 
  - Makayla Whitney
  - Joe Swinehart
  - Janette Avelar
  - David Fainstein
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lab 1 - Data Structures

Run the above code

1. From the model results:

Extract the qr tolerance (tol).
Extract the term labels from the model.
hint: Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.

```{r DS Part 1}
# Inhereted code
set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
              	   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))

#extracting the qr tolerance
tolerance <- m$qr$tol

#extracting term labels
term_labels <- attributes(m$terms)
car_labels <- term_labels$variables

```

Data Structures 
2. From the list
Use at least two different methods to extract m.
Extract the third column of m. Maintain the dimensions (matrix structure).
Extract the score for student 7.
```{r extracting m}
r <- l[["a"]][["m"]]
r
```

```{r extracting m again}
l$a$m
```

```{r extracting the third column}
as.matrix(r[ , 3])
```

```{r extracting a score for 7}
l[["b"]][["score"]][[7]]
```

## Lab 1 - Loops 

3. Use the “airquality” dataset, which is part of base R. Split it by Month
```{r Q3}
aq <- airquality
aq_mo <- split(aq, aq$Month)
```

4. Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

```{r}
means <- vector("list", length(aq_mo))

for(i in seq_along(means)) {
    means[[i]] <- mean(aq_mo[[i]]$Ozone, na.rm = TRUE)
}

View(means)
```

5. Replicate this calculation with lapply, sapply, and vapply
```{r}

lapply(aq_mo, function(x) mean(x$Ozone, na.rm = TRUE))

#sapply(aq_mo, function(x) mean (x$Ozone, na.rm = TRUE), is.double)

vapply(aq_mo, function(x) mean(x$Ozone, na.rm = TRUE), FUN.VALUE = double(1))

```

6. Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop).

```{r}

plots <- lapply(aq_mo, function(x) {
    ggplot(x, aes(Ozone, Solar.R)) +
        geom_point() +
        geom_smooth()
})

```

7. Use a for loop to save the plots to a folder on your computer
```{r}
#dir.create(here::here("plots")) 
filenames <- here::here("plots", 
                        paste0("month", names(aq_mo), ".png"))
filenames

for(i in seq_along(plots)) {
    ggsave(filenames[i],
           plots[[i]],
           device = "png",
           width = 6.5, 
           height = 8)
}

```
